---
title: "Question 3"
subtitle: "Can a company expect to have more financing rounds if they’re in a particular industry?"
output: html_notebook
---

### Analysis

Import cleaned data and used libraries.

```{r}
library(ggplot2)
fundingData <- readRDS("kaggle_data_cleaned.rds")
```


### What do Funding Rounds look like?

The number of rounds ranges from 1 to 18. Most firms had just one round, and the third quartile falls at just 3 rounds. The mean and variance are close to equal, and the data may be an Exponential (blue) distribution or Negative Binomial (red) distribution. The Negative Binomial would have a theoretical backing, where each round of funding is essentially a trial where the company has a (small) chance of proceeding to the next round, otherwise it stops raising venture capital.

```{r}
summary(fundingData$funding_rounds)
print(c("Mean", mean(fundingData$funding_rounds)))
print(c("Var", var(fundingData$funding_rounds)))
hist(fundingData$funding_rounds, prob=TRUE)
lines(1:max(fundingData$funding_rounds), dexp(0:(max(fundingData$funding_rounds)-1), 1/mean(fundingData$funding_rounds)), col = 'blue')
lines(1:max(fundingData$funding_rounds), dnbinom(0:(max(fundingData$funding_rounds)-1), 1, mu=1/mean(fundingData$funding_rounds)), col = 'red')
```



The average amount of funding, when we only include rounds that received funding, increases steadily throughout the rounds, starting at an average of \$7 million in Round A and ending with an average $50 million in Round H. However, the most money raised in total is in Round B, due to the higher average than Round A combined with higher frequency than all later rounds.

```{r}
roundFunding <- fundingData[fundingData["round_total"] > 0,grep("round_.$", colnames(fundingData))]
is.na(roundFunding) <- roundFunding==0
roundFunding.mean <- colMeans(roundFunding, na.rm=TRUE)
roundFunding.sum <- colSums(roundFunding, na.rm=TRUE)
print(roundFunding.mean)
```


Figure x1: The average amount of money raised in each round 
```{r}
barplot(roundFunding.mean)
```

Figure x2: The expecation of how much money can be raised in a particular round
```{r}
barplot(roundFunding.sum)
```


### How does it relate to market?

We restrict the analysis to markets with at least 30 companies recorded.


## ? Why are we using (funding_total_usd, venture, seed) instead of just funding_total_usd?


```{r}
industryList <- c('Travel','Transportation','Games','Music','Video','Finance','Cloud Computing','Health Care','Hospitality','Education')
industryData <- do.call(data.frame, aggregate(cbind(funding_rounds, funding_total_usd, venture, seed)  ~ market, data=fundingData, FUN=function(x) c(mn = mean(x), var = var(x))))
industryData$n <- aggregate(funding_total_usd  ~ market, data=fundingData, FUN=length)$funding_total_usd
industryData <- subset(industryData, market %in% industryList)
summary(industryData$funding_rounds.mn)
```

Variance does not seem to be consistent between industries.

```{r}
#Variance in rounds is not equal
summary(industryData$funding_rounds.var)
hist(industryData$funding_rounds.var)
```


```{r, echo=FALSE}
## This doesn't address any of the questions we're investigating

# Round to seed funding has no trend
#plot(industryData$funding_rounds.mn, industryData$seed.mn)

# Round to venture funding is linear.
#plot(industryData$funding_rounds.mn, industryData$venture.mn)

```