---
title: "Question 3"
date: "2/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Is the average amount of money raised different depending on the industry?

First we will do some exploration on the cleaned dataset.

## 1. Check summary statistics. 

```{r}
require(dplyr)
kaggle_data_cleaned <- readRDS("kaggle_data_cleaned.rds")
summary(kaggle_data_cleaned)
```
Since there's a lot of information here lets remove the unnecessary information. Here our main focus is the `market` and the `funding_total_usd` for each company.

```{r}
data <- kaggle_data_cleaned %>%
  dplyr::select(market, funding_total_usd)
dim(data)
summary(data)
```

Now we can clearly see the more prominent markets that companies from this dataset operate in and some information about the Total Funding for each company.

For a more visual representation of the distribution of data points across the different markets:
```{r}
#frequency of companies across markets in descending order
sorted_markets <- sort(table(data$market), decreasing=TRUE)

#taking top n most popular markets of operation
n=20
popular_markets <- sorted_markets[1:n]
par(mar=c(10, 5, 1, 1)) #adjusting margins
barplot(popular_markets, las=2)

```
  
It looks like there's clearly a larger portion of companies that are in the Software and Biotechnology markets which we will have to keep in mind.

### Removing Outliers

Let's now take a look at the Total Funding variable and generate boxplots for each of the most popular markets and their total funding per company. We find many outliers to deal with. To ensure that our tests are accurate we remove some of the prominent outliers.  
```{r}
#total funding data
par(mar=c(3, 5, 1, 1)) 
boxplot(data$funding_total_usd,  main="Total Funding boxplot")

#total funding data for each market
popular_markets = as.data.frame(popular_markets)
popular_markets_data <- filter(data, data$market %in% popular_markets$Var1)
popular_markets_data = na.omit(popular_markets_data)

#drop unused levels
popular_markets_data$market <- droplevels(popular_markets_data$market)

par(mar=c(10, 5, 1, 1)) 
boxplot(popular_markets_data$funding_total_usd~popular_markets_data$market,las=2, xlab=NULL, ylab=NULL, main="Popular Markets - Funding total boxplots")

#saving then removing the outliers for total data
outliers <- boxplot(data$funding_total_usd, plot = FALSE)$out

#number of outliers according to boxplot
#length(outliers)
x<-data
x<- x[-which(x$funding_total_usd %in% outliers),]
par(mar=c(3, 5, 1, 1)) 
boxplot(x$funding_total_usd, main="Total Funding boxplot (outliers removed)")

#plot the popular markets boxplots again
popular_markets_data <- filter(x, x$market %in% popular_markets$Var1)
popular_markets_data = na.omit(popular_markets_data)

#drop unused levels
popular_markets_data$market <- droplevels(popular_markets_data$market)

# distribution of data across top 20 popular markets
par(mar=c(10, 5, 1, 1)) 
boxplot(popular_markets_data$funding_total_usd~popular_markets_data$market, data=popular_markets_data, las=2, xlab=NULL, ylab=NULL ,main="Popular Markets - Funding total boxplots (outliers removed)")
```
It looks like there are quite a large number of outliers outside the range as we cannot see any clear boxplots initially.  

After removal of outliers we can now observe the variances across the top 20 markets regarding their total funding values.
```{r}
summary(popular_markets_data)
print(paste(c("Market", "Variance (within)", "Mean")))
for(i in popular_markets$Var1){
  temp = popular_markets_data[popular_markets_data$market == i,]
  print(paste(c(i, var(temp$funding_total_usd), mean(temp$funding_total_usd))))
}
```

## 2. Check ANOVA assumptions

Check if ANOVA assumptions are valid for average amounts of money raised for each industry (Question 1)

#### a. Equal Variances (Homoscedasticity or homegeity of variance)


```{r}
#Homogeneity of Variances
bartlett.test(popular_markets_data$funding_total_usd~popular_markets_data$market, data=popular_markets_data)

library(HH)
hov(popular_markets_data$funding_total_usd~popular_markets_data$market, data=popular_markets_data)
hovPlot(popular_markets_data$funding_total_usd~popular_markets_data$market, data=popular_markets_data)
```
The variances of each of the most populat markets are all not equal.

#### b. Normally distributed means

```{r}
#frequency distribution of total funding amounts
hist(popular_markets_data$funding_total_usd)

#plotting means of samples (for each category)
means_data = c()
for(i in popular_markets$Var1){
  temp = popular_markets_data[popular_markets_data$market == i,]
  means_data <- c(mean(temp$funding_total_usd), means_data)
}
means_data = as.data.frame(means_data)
hist(means_data, breaks = 6)

#if data is normal then points should form a straight line
qqnorm(popular_markets_data$funding_total_usd, main="Total Funding Data")
qqline(popular_markets_data$funding_total_usd)


#qq plot for each 
for(i in popular_markets$Var1){
  temp = popular_markets_data[popular_markets_data$market == i,]
  qqnorm(temp$funding_total_usd, main = `i`)
  qqline(temp$funding_total_usd)
}

```
Need to look into:  

Several methods for evaluate normality, including the Kolmogorov-Smirnov (K-S) normality test and the Shapiro-Wilk’s test.  

The null hypothesis of these tests is that “sample distribution is normal”. If the test is significant, the distribution is non-normal.  

Shapiro-Wilk’s method is widely recommended for normality test and it provides better power than K-S. It is based on the correlation between the data and the corresponding normal scores (Ghasemi and Zahediasl 2012).  

Note that, normality test is sensitive to sample size. Small samples most often pass normality tests. Therefore, it’s important to combine visual inspection and significance test in order to take the right decision.  

#### c. Independent samples

Assuming independence of samples for this case. We have no further information on the data collection methods to confirm independence.That being said no two groups consists of the same company appearing in multiple markets and all companies are expected to be independent startups with no collaboration or affiliation with each other.

## 3. Perform ANOVA

```{r}
summary(aov(popular_markets_data$funding_total_usd~popular_markets_data$market))
```
**ANOVA results in rejecting the null hypothesis that the average total funding in the top `r n` market groups is the same**


Alternatives to ANOVA for unequal variance are:

Here are some options:

transformations
Welch ANOVA
weighted least squares
robust regression
heteroscedasticity consistent standard errors
bootstrap
Kruskal-Wallis test
ordinal logistic regression

[Welch's ANOVA](http://ritsokiguess.site/docs/2017/05/19/welch-analysis-of-variance/) 
(One-way analysis of means (not assuming equal variances)):
```{r}
#library(rstatix)
#welch_anova_test(popular_markets_data$funding_total_usd~popular_markets_data$market)
oneway.test(popular_markets_data$funding_total_usd~popular_markets_data$market)
```