---
title: "Question 2"
subtitle: "Can we describe the relationship between the amount of seed funding and the year of first funding received?"
author: "Jonathan Kerr"
date: "18/02/2021"
output: html_document
---

*Our question is based on exploring if the amounts of investments going into start-up companies over the years have steadily increased or not. We will explore if the relationship between the amount of seed funding and the year of obtaining those funds is linear or some other form of relationship.*

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
kaggle_data_cleaned <- readRDS("kaggle_data_cleaned.rds")
```

Let's take a quick look at the "first_funding_at" data.  

```{r}
# EDA
eda <- kaggle_data_cleaned %>% 
  dplyr::select(first_funding_at) %>% 
  dplyr::arrange(first_funding_at)
head(eda)
```

Let's bucket the 'first_funding_at' by year and filter bad data (funding year 0011) and also use the data that we have adjusted for inflation. 

```{r}
first_year <- 1980
first_funding_date <- kaggle_data_cleaned %>% 
  mutate(first_funding_at = as.numeric(substring(first_funding_at, 1,4)) ) %>% 
  filter(first_funding_at >= first_year) %>% 
  filter(first_funding_at <= 2014)# %>%

model <- lm(formula = inflationAdjustedSeed_1980 ~ first_funding_at, data = first_funding_date)
plot(inflationAdjustedSeed_1980 ~ first_funding_at, data=first_funding_date); abline(model) 
summary(model) 
```
This looks like it could be skewed up by the larger number of rounds in later years. So we can try comparing means instead.

```{r}
mean_compare <- first_funding_date %>% 
    group_by(first_funding_at) %>%
    dplyr::summarize(seed_mean = mean(inflationAdjustedSeed_1980, na.rm=TRUE))

model <- lm(formula = seed_mean ~ first_funding_at, data = mean_compare)
plot(seed_mean ~ first_funding_at, data=mean_compare); abline(model) 
summary(model) 
```
From the above we are able to fit a linear model to the data and it looks like there is a linear trend.
The p-value allows us to reject the null hypothesis that the regression coefficient is zero.  

However, the model is not the best fit given the unsatisfactorily low R-squared value.
Let's take a look at the residuals plots.
```{r}
plot(model)
```
It's quite clear that the constant variance assumption for linear regression is not met which gives us enough reason to invalidate our linear model.

**We realized that when dealing with very large values like monies in company funding we can not capture the necessary relationship to model the data and make relative comparisons without making a transformation to the data.**

There are two way we can work with this data.
1. Use a log transform on the fields that include funding amounts and perform linear regression, or
2. Use Poisson regression to better describe this type of data. 

## 1. Log transforms on the seed funding data and exploring seed funding chance.    

### Can we seperate the chance of seed funding from the amount?

Let us transform our data taking the log(seed_funding) for the companies that received seed funding amounts.
```{r}
# Add the required new columns
decompData <- first_funding_date
decompData$seed <- decompData$inflationAdjustedSeed_1980
decompData$got_seed <- decompData$seed > 0
decompData$log_seed <- log(decompData$seed)
decompData[is.infinite(decompData$log_seed),]$log_seed <- -9999999999999
decompData_with_seed <- decompData[decompData$got_seed == TRUE,]
data.frame(decompData$first_funding_at, decompData$inflationAdjustedSeed_1980, decompData$log_seed, decompData$log_seed)
```

Let us look at the transformed seed data over time.
```{r}
# Model seed chance
annualData <- do.call(data.frame, aggregate(cbind(seed, got_seed, log_seed)  ~ first_funding_at, data=decompData, FUN=mean))
model.seed_chance <- lm(formula = got_seed ~ first_funding_at, data = annualData[annualData$first_funding_at >= 1990,])
summary(model.seed_chance)
plot(got_seed ~ first_funding_at, data=annualData); abline(model.seed_chance) 
```
*There does not appear to be a change in the amount of seed funding given over time. There is no significant linear relationship.*  

However, the inflation-adjusted amount of seed money raised increases over time with an average of $105.5(thousand) a year,  at the 0.05 significance level.
```{r}
# Model seed amount
annualData.with_seed <- do.call(data.frame, aggregate(cbind(seed, got_seed, log_seed)  ~ first_funding_at, data=decompData_with_seed, FUN=mean))
model.seed_amount <- lm(formula = seed ~ first_funding_at, data = annualData.with_seed)
summary(model.seed_amount)
plot(seed ~ first_funding_at, data=annualData.with_seed); abline(model.seed_amount) 
```

*The residuals deviate significantly from normal on the high end, so this model may not be valid. (As shown below.)*

```{r}
plot(model.seed_amount)
```

Here we also see a case of Simpsons Paradox, where grouping the data reverses the apparent trend. If we look at all non-zero data points, not grouped by year, we get a negative relationship, as shown below.

```{r}
# Model seed amount
model.seed_amount_ungrouped <- lm(formula = seed ~ first_funding_at, data = decompData_with_seed)
summary(model.seed_amount_ungrouped)
plot(seed ~ first_funding_at, data=decompData_with_seed, ylim=c(0, 10000000)); abline(model.seed_amount_ungrouped)
```

Closer examination shows that this is caused by a growing skewness in the data. Note how the higher quantiles grow more quickly in recent years, while the lower remain stable. Skewness also clearly grows year to year.


```{r}
library(e1071) 
annualData.quants <- do.call(data.frame, aggregate(seed  ~ first_funding_at, data=decompData_with_seed, FUN=function(x){quantile(x, probs=c(0.25, 0.5, 0.75, 0.9))}))
x <- cbind(annualData.quants$first_funding_at, annualData.quants$first_funding_at, annualData.quants$first_funding_at, annualData.quants$first_funding_at)
y <- cbind(annualData.quants$seed.25., annualData.quants$seed.50., annualData.quants$seed.75., annualData.quants$seed.90. )
matplot(x, y, type="o", pch=1)

annualData.skew <- do.call(data.frame, aggregate(seed  ~ first_funding_at, data=decompData_with_seed, FUN=skewness))
plot(seed ~ first_funding_at, data=annualData.skew)


```

Linear tests confirm, there is not evidence to reject that the 25th quantile is constant over time, while there is enough to reject that the 90th quantile is constant at the 0.05 significance level.

```{r}
model.25q <- lm(seed.25. ~ first_funding_at, data=annualData.quants)
summary(model.25q)

model.90q <- lm(seed.90. ~ first_funding_at, data=annualData.quants)
summary(model.90q)
```

Looking at the inflation-adjusted log of seed money makes the trend more clear, with seed funding growing at about 9\% per year at the 0.01 significance level.
```{r}
# Model log seed amount
model.seed_amount_log <- lm(formula = log_seed ~ first_funding_at, data = annualData.with_seed, na.action=na.omit)
plot(log_seed ~ first_funding_at, data=annualData.with_seed); abline(model.seed_amount_log) 
print(summary(model.seed_amount_log))
```
## 2. Use Poisson regression to better describe this type of data.

Let us try Poisson regression *without* averaging by year.
```{r}
# Model poisson seed
model.seed_amount_pois <- glm(formula = seed ~ first_funding_at, data = first_funding_date, family=poisson, na.action=na.omit)
plot(seed ~ first_funding_at, data=first_funding_date, ylim=c(0,5000000))
points(first_funding_date$first_funding_at, exp(predict(model.seed_amount_pois)), type="l", col="red", lwd=2)
print(summary(model.seed_amount_pois))
```


This model also has better behaved residuals, appearing mostly normal and shows lower levels of non-constant variance.
```{r}
plot(model.seed_amount_log)
```

Let us try Poisson regression *with* averaging by year.
```{r}
# Model poisson seed
mean_compare_pois <- first_funding_date %>% 
    group_by(first_funding_at) %>%
    dplyr::summarize(seed_mean = mean(inflationAdjustedSeed_1980, na.rm=TRUE))

model.seed_amount_pois <- glm(formula = seed_mean ~ first_funding_at, data = mean_compare_pois, family=poisson, na.action=na.omit)
plot(seed_mean ~ first_funding_at, data = mean_compare_pois, ylim=c(0,5000000))
points(mean_compare_pois$first_funding_at, exp(predict(model.seed_amount_pois)), type="l", col="red", lwd=2)
print(summary(model.seed_amount_pois))
```

### THE FOLLOWING CAN BE DELETED. We are not using polynomial regression to stay within the scope of this class.
```
#POLYNOMIAL REGRESSION
#https://stats.stackexchange.com/questions/258307/raw-or-orthogonal-polynomial-regression for discussion on orthogonal polynomials.
p2model <- lm(seed_mean ~ poly(first_funding_at, 2), data = mean_compare) #poly(first_funding_at, 2, raw=TRUE)
p3model <- lm(seed_mean ~ poly(first_funding_at, 3), data = mean_compare)

summary(p2model)
summary(p3model)

print(anova(p2model, p3model))

plot(seed_mean ~ first_funding_at, data=mean_compare)
points(mean_compare$first_funding_at, predict(p2model), type="l", col="red", lwd=2)
points(mean_compare$first_funding_at, predict(p3model), type="l", col="blue", lwd=2)
```