---
title: "Question 4"
author: "Jonathan Kerr"
subtitle: "Does the proportion of companies that get seed funding also get venture funding?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( echo = TRUE )
require( dplyr )
kaggle_data_cleaned <- readRDS( "kaggle_data_cleaned.rds" )
```

## What proportion of companies get seed funding?

```{r}
companies.num <- nrow( kaggle_data_cleaned )
seed.num <- nrow( kaggle_data_cleaned %>% filter( seed > 0 ) )
cat( round( ( seed.num/companies.num ) * 100, 0 ), "% of the companies received seed funding", sep = "" )
```

## Of the companies that got seed funding, what proportion also got venture funding?

```{r}
seed.and.venture.num <- nrow( kaggle_data_cleaned %>% filter( seed > 0 ) %>% filter( venture > 0 ) )
cat( round( ( seed.and.venture.num/seed.num ) * 100, 0 ), "% of the companies that received seed funding also received venture funding.", sep = "" )
```

## What proportion of all companies got venture funding?
```{r}
venture.all <- nrow( kaggle_data_cleaned %>% filter( venture > 0 ) )
cat( round( ( venture.all/companies.num ) * 100, 0 ), "% of all the companies sampled recieved venture funding.", sep = "" )
```

## What proportion of all companies got seed and venture funding?
```{r}
cat( round( ( seed.and.venture.num/companies.num ) * 100, 0 ), "% of the companeies that had seed funding also had venture funding.", sep = "" )
```


```{r}
venture.noseed.num <- nrow( kaggle_data_cleaned %>% filter( seed == 0 ) %>% filter( venture > 0 ) )
cat( round( ( venture.noseed.num/companies.num ) * 100, 0 ), "% of the companeies that didn't have seed funding also had venture funding.", sep = "" )
```


```{r, echo=FALSE}
  ## Note to classmates: We probably don't need to include above statements.  I suspect the following would cover it.
```


## Venn Diagram

Let's begin by looking at the proportion of companies that had seed and venture rounds.

```{r, echo=FALSE}
#install.packages("BiocManager")
#BiocManager::install("limma")

seed.v <- kaggle_data_cleaned %>% select(seed) %>% mutate(seed = as.numeric(seed > 0) ) 
venture.v <- kaggle_data_cleaned %>% select(venture) %>% mutate(venture = as.numeric(venture > 0) ) 

library( limma )
g <- cbind(
  seed = seed.v, 
  venture = venture.v )
vennDiagram( round( vennCounts( g ) / nrow( seed.v ) * 100, 0 ),
             main="Funding sources (%)",
             names = c("Seed", "Venture"),
             counts.col=c("blue", "blue"),
             circle.col = c("blue", "red"))
```

### If you did a seed round, how likely are you to do a venture round?

As we see in the diagram, not all companies do a seed round, nor do all companies do a venture round.  By definition, a seed round takes place before a venture round.  So if a seed round were to occur, what would be the probability of also doing a venture round?  

We know by Bayes Theorum that P(Venture|Seed) = P(Venture \cap Seed) / P(Seed) = .09/.32 = 0.28.  This means that if a company was to have a seed round, they'd have a 28% chance of also doing a venture round.

### If you didn't do a seed round, how likely are you to do a venture round?

Conversely, if a company didn't do a seed round, the we need to consider the Probability that there wasn't a seed round: P(!Seed) = 1 - 0.32 = 0.68.  Using the same formula to calculate the probability of a venture, given they didn't do a seed round: P(Venture | !Seed) =  P(Venture \cap !Seed) / P(!Seed) = .55/.68 = .81.  This is means that a company that doesn't do a seed round, has an 81% chance of getting venture funding.  


```{r, echo=FALSE}
Pv <- .55 + .09
Ps <- .23 + .09
Psv <- .09
PnotS <-  1 - Ps
PVnotS <- .55

#Psv/Ps
#PVnotS/PnotS  
```







