---
title: "Question 3"
author: "Sai Muktevi"
date: "2/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Is the average amount of money raised different depending on the industry?

First we will do some exploration on the cleaned dataset.

### 1. Check summary statistics. 

```{r}
require(dplyr)
kaggle_data_cleaned <- readRDS("kaggle_data_cleaned.rds")
summary(kaggle_data_cleaned)
```
Since there's a lot of information here lets remove the unnecessary information. Here our main focus is the `market` and the `funding_total_usd` for each company.

```{r}
data <- kaggle_data_cleaned %>%
  select(market, funding_total_usd)
dim(data)
summary(data)
```

Now we can clearly see the more prominent markets that companies from this dataset operate in and some information about the Total Funding for each company.

To get an idea of the range of funding and the distribution lets plot a few more graphs on these two variables to get a closer look at the data.

```{r}
#frequency of companies across markets in descending order
sorted_markets <- sort(table(data$market), decreasing=TRUE)

#taking top n most popular markets of operation
n=20
popular_markets <- sorted_markets[1:n]
par(mar=c(10, 5, 1, 1)) #adjusting margins
barplot(popular_markets, las=2)

```
It looks like there's clearly a larger portion of companies that are in the Software and Biotechnology markets which we will have to keep in mind.

Let's now take a look at the Total Funding variable.
```{r}
```


### 2. Check ANOVA assumptions

Check if ANOVA assumptions are valid for mean amounts of money raised for each industry (Question 1)
1. Equal Variances
2. Normally distributed
3. Independent samples

### 3. Perform ANOVA
