---
title: "Financing Rounds by Industry"
subtitle: "Can a company expect to have more financing rounds if they’re in a particular industry?"
date: "2/27/2021"
output: html_document
---
## Introduction
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

```{r, echo = T}
#importing Start-up Investments Crunchbase data set.
#Source: https://www.kaggle.com/arindam235/startup-investments-crunchbase

investments <- read.csv("investments_VC.csv", header = TRUE)
dim(investments)

allMarkets <- investments[c("market", "funding_rounds")]
dim(allMarkets)

markets <- c(" Travel ", " Transportation ", " Games ", " Music ", " Video ", " Finance ", " Cloud Computing ", " Health Care ", " Hospitality ", " Education ")

#filtered to columns of interest, markets of interest
d <- allMarkets[which(allMarkets$market %in% markets), ]
dim(d)
summary(d)

```


### What do Funding Rounds look like?

The number of rounds ranges from 1 to 18. Most firms had just one round, and the third quartile falls at just 3 rounds. The mean and variance are close to equal, and the data may be an Exponential (blue) distribution or Negative Binomial (red) distribution. The Negative Binomial would have a theoretical backing, where each round of funding is essentially a trial where the company has a (small) chance of proceeding to the next round, otherwise it stops raising venture capital.## Performing Analysis

```{r, echo = T}


markets <- c(" Travel ", " Transportation ", " Games ", " Music ", " Video ", " Finance ", " Cloud Computing ", " Health Care ", " Hospitality ", " Education ")
#plotting means of samples (for each category)
means_data = c()
for(i in markets){
  temp = d[d$market == i,]
  means_data <- c(mean(temp$funding_rounds), means_data)
}
means_data = as.data.frame(means_data)
markets = as.data.frame(markets)
means <- data.frame(markets, means_data)
View(means)
ggplot(means, aes(x = reorder(markets, -means_data), y = means_data)) + geom_bar(stat = "identity") + labs(title = "Average Number of Rounds by Industry", x = "", y = "")
```

Checking assumption of equal variance: 

```{r, echo = T}
boxplot <- ggplot(d, aes(x = market, y = funding_rounds))
boxplot + geom_boxplot()

```

Performing ANOVA F-Test:
``` {r, echo = T}
market <- d$market
rounds <- d$funding_rounds
summary(aov(rounds ~ factor(market)))

```
