---
title: "Startup Funding Exploratory Analysis"
output: html_notebook
---


First, we import the data, converting dates and numeric values where necessary.

```{r}
library(blscrapeR)
# Import
data <- read.csv("investments_VC.csv", strip.white=TRUE)

# Convert Dates
date_cols <- c("founded_at","first_funding_at","last_funding_at")
data[, date_cols] <- lapply(data[ , date_cols], as.Date)

# Convert Factors
factor_cols <- c("category_list", "market", "status", "country_code", "state_code", "region", "city")
data[, factor_cols] <- lapply(data[ , factor_cols], as.factor)

# Convert numerics
data$funding_total_usd <- as.numeric(sapply(data$funding_total_usd, function(x){gsub("[ ,-]", "", x)}, USE.NAMES=FALSE))
data$funding_total_usd[is.na(data$funding_total_usd)] <- 0

# Remove blank rows and missing status
data <- data[!(data$name == "" | is.na(data$name)),]
data <- data[data$status != "",]
data <- data[data$funding_total_usd != 0,]
data <- data[data$market != "",]

# At funding years
#data$first_funding_year <- format(as.Date(data$first_funding_date, format="%d/%m/%Y"),"%Y")
#data$last_funding_year <- format(as.Date(data$last_funding_date, format="%d/%m/%Y"),"%Y")

# Only USA
data <- data[data$country_code == "USA",]

# After 1980
data <- data[data$founded_year >= 1980 & !is.na(data$founded_year) ,]



summary(data)
```

Next, we confirm some of the data. All the funds data adds up to the total, but venture money and round money do not perfectly align. It appears that in most cases, the sum of round totals adds up to be the venture funding, but sometimes round data is missing or see data is included. A new round_total variable is create.

```{r}
# Count Na's as 0
fundingData <- data[,c("seed", "venture", "equity_crowdfunding", "undisclosed", "convertible_note", "debt_financing", "angel", "grant", "private_equity","post_ipo_equity","post_ipo_debt","secondary_market","product_crowdfunding")]
fundingData[is.na(fundingData)] <- 0

# Sums
actual_total = apply(fundingData, 1, sum)
print(summary(data$funding_total_usd - actual_total))


roundData <- data[c("round_A", "round_B", "round_C", "round_D", "round_E", "round_F", "round_G", "round_H")]
roundData[is.na(roundData)] <- 0
data$ round_total <- apply(roundData, 1, sum)
diff <- data$venture - data$round_total

print(summary(diff))

plot(data$venture, data$round_total)
abline(0,1)

# Create inflation adjusted table based of 1980 dollars
inflationlookup <- inflation_adjust(1980)
data$inflationAdjustedSeed_1980 <- data$seed * 
        inflationlookup[match(format(data$first_funding_at, format="%Y"), inflationlookup$year),]$adj_value

```
```{r}
saveRDS(data, "kaggle_data_cleaned.rds")
write.csv(data, "kaggle_data_cleaned.csv")
```

